### 2011-02-23 proposal/paper.tex
added some existing system des

\section{Current System}
We are currently working to get the T-verifier code running on our
systems, with inputs from Xian Li. So the descriptions below lacks some required
details and makes some assumptions.

>>>>

\section{Current System}
Current system for truthfulness verification is called T-verifier, which uses two phase methods for truthfulness verification of statements. Each of these two phases rely heavily on search results returned by popular search engines.

T-verifier takes the doubtful statements as input from the user along with

We are currently working to get the T-verifier code running on our
systems, with inputs from Xian Li. So the descriptions below lacks some required
details and makes some assumptions.
